\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2015-04-18 doc/USER_MANUAL/manual_SPECFEM3D_Cartesian.tex
cleaned the demo codes and mentioned them in the manual

The software package SPECFEM3D Cartesian simulates seismic wave propagation
at the local or regional scale based upon the spectral-element method
(SEM). The SEM is a continuous Galerkin technique \citep{TrKoLi08,PeKoLuMaLeCaLeMaLiBlNiBaTr11},
which can easily be made discontinuous \citep{BeMaPa94,Ch00,KoWoHu02,ChCaVi03,LaWaBe05,Kop06,WiStBuGh10,AcKo11};
it is then close to a particular case of the discontinuous Galerkin
technique \citep{ReHi73,LeRa74,Arn82,JoPi86,BoMaHe91,FaRi99,HuHuRa99,CoKaSh00,GiHeWa02,RiWh03,MoRi05,GrScSc06,AiMoMu06,BeLaPi06,DuKa06,DeSeWh08,PuAmKa09,WiStBuGh10,DeSe10,EtChViGl10},
with optimized efficiency because of its tensorized basis functions
\citep{WiStBuGh10,AcKo11}. In particular, it can accurately handle
very distorted mesh elements \citep{OlSe11}.\\

@@

>>>>

The software package SPECFEM3D Cartesian simulates seismic wave propagation
at the local or regional scale and performs full waveform imaging (FWI) or adjoint tomography based upon the spectral-element method
(SEM). The SEM is a continuous Galerkin technique \citep{TrKoLi08,PeKoLuMaLeCaLeMaLiBlNiBaTr11},
which can easily be made discontinuous \citep{BeMaPa94,Ch00,KoWoHu02,ChCaVi03,LaWaBe05,Kop06,WiStBuGh10,AcKo11};
it is then close to a particular case of the discontinuous Galerkin
technique \citep{ReHi73,LeRa74,Arn82,JoPi86,BoMaHe91,FaRi99,HuHuRa99,CoKaSh00,GiHeWa02,RiWh03,MoRi05,GrScSc06,AiMoMu06,BeLaPi06,DuKa06,DeSeWh08,PuAmKa09,WiStBuGh10,DeSe10,EtChViGl10},
with optimized efficiency because of its tensorized basis functions
\citep{WiStBuGh10,AcKo11}. In particular, it can accurately handle
very distorted mesh elements \citep{OlSe11}.\\

@@

\chapter{\label{cha:developers}Information for developers of the code, and for people who want to learn how the technique works}

You can get a very simple 1D version of a demo code (there is one in Fortran and one in Python):\\

git clone --recursive https://github.com/geodynamics/specfem1d.git\\

\noindent We also have simple 3D demo source codes that implement the SEM in a single, small program, in directory\\
utils/small\_SEM\_solvers\_in\_Fortran\_and\_C\_without\_MPI\_to\_learn of the specfem3d package.
They are useful to learn how the spectral-element method works, and how to write or modify a code to implement it.
Also useful to test new ideas by modifying these simple codes to run some tests.\\

\noindent For information on how to contribute to the code, i.e., for how to make your modifications, additions or improvements part of the
official package, see https://github.com/geodynamics/specfem3d/wiki .
